Quality Definitions of Qualities

### 2020-01-19 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
definition clean ups

\begin{defn} \label{Correctness_Selected}
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  \wss{Is this verbatim from
    the original source?  If not, we should show those parts that are verbatim
    in quotes, so that readers know the parts that were developed by us.}
  \oo{Yes, verbatim}

\end{defn}

\begin{defn}
  The degree to which a system is free from defects in its specification, design, and implementation, is its correctness \citep{wilson2009quality}.  \oo{Need to verify this definition, still searching for this paper}
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with pdf} \wss{Great!  Did you add the Mccall paper to the pub repo?}
\oo{I will}
\end{defn}

@@

Definition~\ref{Correctness_Selected} rephrased: A program is functionally correct if it behaves according to its stated specifications  \oo{Proposed definition updated to Ghezzi's}

@@

Definition~\ref{Defn_Verifiability1}:
Verifiability means that you should be able to write a set of tests that can demonstrate that the delivered system meets each specified requirement.

@@

\begin{defn}
  Validation refers to a different set of tasks that ensure that the software
  that has been built is traceable to customer requirements.{to be removed, its from geeksforgeeks}
\end{defn}

@@

>>>>

\begin{defn} \label{Correctness_Selected}
  A program is functionally correct if it behaves according to its stated
  functional specifications \citep{GhezziEtAl2003}.  	
\end{defn}

\begin{defn}
  The degree to which a system is free from faults in its specification, design, and 
  implementation \citep{mcconnell2004code}.
\end{defn}

@@

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. 
\end{defn}

@@

Definition~\ref{Correctness_Selected} rephrased: A program is correct if it
behaves according to its stated specifications.

@@

\begin{defn}
	The evaluation of whether or not a product, service, or result complies with
	a regulation, requirement, specification, or imposed condition \citep{project2017guide}
	\oo {verification definition}
\end{defn}

\begin{defn}
	By verification, we mean all activities that are undertaken to ascertain that the
	software meets its objectives \citep{GhezziEtAl2003}.
\end{defn}
\noindent \textbf{Proposed Definition}

Definition~\ref{Defn_Verifiability1} rephrased:
Verifiability is the extent to which a set of tests can be written and executed, to demonstrate
that the delivered system meets each specified requirement.

@@

\begin{defn}
  The assurance that a product, service, or result meets the needs of the customer and other identified
  stakeholders \citep{project2017guide}.
\end{defn}

@@

\subsection{\notdone{Testability} \oo{owner}}

\begin{defn}
	The degree to which you can unit-test and system-test a system;
	the degree to which you can verify that the system meets its requirements \citep{mcconnell2004code}.
\end{defn}

\begin{defn}
	Code possesses the characteristic testability to the extent that it
    facilitates the establishment of verification criteria and supports
    evaluation of its performance \citep{boehm1976quantitative}
\end{defn}
